The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2016-02-15 script/en/chapters/movies.tex
Corrected typos and overfull hbox; congruent index (no redundancy in wording; adjectives in lowercase in German; all normal words in lowercase in English)

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{appendix-movies}{}%neu
\section{Movies and Fictional Literature with Relation to Cryptography}
\label{s:appendix-movies}
% {\bf movies and literature related to cryptography}(see appendix \ref{s:appendix-movies})
\index{Movies}
\index{Literature}

@@

\item[\textrm{[Robinson1992]}] \index{Robinson 1992}
    Directed by Phil Alden Robinson, \\
    {\em Sneakers}, Universal Pictures Film, 1992. \\
    In this movie the ``sneakers'', computer experts under their boss Martin
    Bishop, try to get back the deciphering box SETEC from the ``bad guys''.
    SETEC, invented by a genius mathematician before he was killed, allows to
    decrypt all codes from any nation. \\
    In the movie the code is not described in any way%
    \footnote{
       Leonard Adleman (the "A" within RSA) worked as mathematical consultant
       for ``Sneakers''. He describes the funny story about his contribution
       at his homepage 
       \url{http://www.usc.edu/dept/molecular-science/fm-sneakers.htm}.
       It is assumed that the cipher used everywhere is RSA.      
       According to that within the chip a fast, unknown factorization
       method\index{Factorization} is implemented.
    }.\\

@@

\item[\textrm{[Stephenson1999]}] \index{Stephenson 1999}
    Neal Stephenson, \\
    {\em Cryptonomicon}, Harper, 1999. \\
    This very thick novel deals with cryptography both in WW2 and today.
    The two heroes from the 40ies are the excellent mathematician and
    cryptanalyst Lawrence Waterhouse, and the overeager and 
    morphine addicted US marine Bobby Shaftoe. 
    They both are members of the special allied unit 2702, which tries
    to hack the enemy's communication codes and at the same time to
    hide the own existence. \\
    This secretiveness also happens in the present plot, where the 
    grandchildren of the war heroes -- the dedicated programmer  
    Randy Waterhouse and the beautiful Amy Shaftoe -- team up. \\
    Cryptonomicon is notably heavy for non-technical readers in parts.
    Several pages are spent explaining in detail some of the concepts
    behind cryptography.
    Stephenson added a detailed description of the Solitaire cipher
    (see chapter~\ref{Further-PaP-methods}), a paper and pencil encryption
    algorithm\index{Paper and pencil methods} developed by Bruce Schneier
    which is called ``Pontifex'' in the book. Another, modern algorithm
    called ``Arethusa'' is not explained in detail.\\

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{appendix-Learn-NT}{}
\section{Learning Tool for Elementary Number Theory}
    \label{s:appendix-Learn-NT}  
    \index{NT, Learning Tool for Number Theory}%
    \index{Educational tool NT}%

>>>>

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{appendix-movies}{}%neu
\section{Movies and Fictional Literature with Relation to Cryptography}
\label{s:appendix-movies}
% {\bf movies and literature related to cryptography}(see appendix \ref{s:appendix-movies})
\index{movies}
\index{literature}

@@

\item[\textrm{[Robinson1992]}] \index{Robinson 1992}
    Directed by Phil Alden Robinson, \\
    {\em Sneakers}, Universal Pictures Film, 1992. \\
    In this movie the ``sneakers'', computer experts under their boss Martin
    Bishop, try to get back the deciphering box SETEC from the ``bad guys''.
    SETEC, invented by a genius mathematician before he was killed, allows to
    decrypt all codes from any nation. \\
    In the movie the code is not described in any way%
    \footnote{
       Leonard Adleman (the "A" within RSA) worked as mathematical consultant
       for ``Sneakers''. He describes the funny story about his contribution
       at his homepage 
       \url{http://www.usc.edu/dept/molecular-science/fm-sneakers.htm}.
       It is assumed that the cipher used everywhere is RSA.      
       According to that within the chip a fast, unknown factorization
       method\index{factorization} is implemented.
    }.\\

@@

\item[\textrm{[Stephenson1999]}] \index{Stephenson 1999}
    Neal Stephenson, \\
    {\em Cryptonomicon}, Harper, 1999. \\
    This very thick novel deals with cryptography both in WW2 and today.
    The two heroes from the 40ies are the excellent mathematician and
    cryptanalyst Lawrence Waterhouse, and the overeager and 
    morphine addicted US marine Bobby Shaftoe. 
    They both are members of the special allied unit 2702, which tries
    to hack the enemy's communication codes and at the same time to
    hide the own existence. \\
    This secretiveness also happens in the present plot, where the 
    grandchildren of the war heroes -- the dedicated programmer  
    Randy Waterhouse and the beautiful Amy Shaftoe -- team up. \\
    Cryptonomicon is notably heavy for non-technical readers in parts.
    Several pages are spent explaining in detail some of the concepts
    behind cryptography.
    Stephenson added a detailed description of the Solitaire cipher
    (see chapter~\ref{Further-PaP-methods}), a paper and pencil encryption
    algorithm\index{paper and pencil methods} developed by Bruce Schneier
    which is called ``Pontifex'' in the book. Another, modern algorithm
    called ``Arethusa'' is not explained in detail.\\

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{appendix-Learn-NT}{}
\section{Learning Tool for Elementary Number Theory}
    \label{s:appendix-Learn-NT}  
    \index{NT, Learning Tool for Number Theory}%
    \index{educational tool NT}%
